---
title: "Supplemental Information"
author: Yihao Chen, Li-Na He, Yuanzhe Zhang, Yuelong Shu, Di Zhang, Guangchuang Yu,
  Zhixiang Zuo
date: "2024-04-12"
output:
  pdf_document: 
    latex_engine: lualatex
  html_document:
    df_print: paged
  word_document: default
---
\newpage
# 1 Installation

To install tigeR package, please enter the following command in R:
```{r installation, eval=FALSE}
if (!requireNamespace("devtools", quietly = TRUE))
  install.packages("BiocManager")
devtools::install_github("YuLab-SMU/tigeR")
devtools::install_github("YuLab-SMU/tigeR.data")
```

# 2 Evaluating biomarkers associated with immunotherapy response (Figure 3)

To reproduce the analysis in this document, several extra packages should be library.

```{r library, result='hide', message=FALSE, warning=FALSE}
library(tigeR)
library(tigeR.data)
library(ggplot2)
library(SummarizedExperiment)
library(patchwork)
```

```{r fig.3A, eval=TRUE, message=FALSE, warning=FALSE,fig.width=4, fig.align='center'}
fig.3A <-
  diff_biomk(MEL_PRJEB23709,gene = "CXCL13",type = "Response",
             p.round=3,p.pos = c(0.05,0.60),textcol="black") +
  ylim(0,6.2) +
  ggtitle("MEL-PRJEB23709") +
  ylab("CXCL13 expression (FPKM)") +
  theme(legend.position = "none")
fig.3A
```

```{r fig.3B, eval=TRUE, message=FALSE, warning=FALSE,fig.width=4, fig.align='center'}
fig.3B <-
  diff_biomk(MEL_GSE93157,gene = "CXCL13",type = "Response",
             p.round=3,p.pos = c(0.05,0.355),textcol="black") +
  ylim(2.1,3.6) +
  scale_y_continuous(labels = scales::number_format(accuracy = 1)) +
  ggtitle("MEL-GSE93157") +
  ylab("CXCL13 expression (FPKM)") +
  theme(legend.position = "none")
fig.3B
```

```{r fig.3C, eval=TRUE, message=FALSE, warning=FALSE,fig.width=3.5,fig.align='center'}
fig.3C <-
  roc_biomk(MEL_PRJEB23709,Signature = "CXCL13",textcol = "black",
            auc.pos = c(0.28,0.4))[[2]] +
  ggtitle("MEL-PRJEB23709")
fig.3C
```

```{r fig.3D, eval=TRUE, message=FALSE, warning=FALSE,fig.width=3.5, fig.align='center'}
fig.3D <-
  roc_biomk(MEL_GSE93157,Signature = "CXCL13",textcol = "black",
            auc.pos=c(0.28,0.4))[[2]] +
  ggtitle("MEL-GSE93157")
fig.3D
```

```{r fig.3E, eval=TRUE, message=FALSE, warning=FALSE,fig.width=4, fig.align='center'}
idx_CTLA <- MEL_GSE115821$Therapy=="anti-PD-1"
fig.3E <- 
  diff_biomk(MEL_GSE115821[,MEL_GSE115821$Therapy=="anti-PD-1"],
             gene = "CXCL13",type = "Treatment",p.round=3,
             log_sc = TRUE,p.pos = c(0.05,0.60),textcol="black") +
  ylim(0,6.2) +
  ggtitle("MEL-GSE115821") +
  ylab("CXCL13 expression (FPKM)") +
  theme(legend.position = "none")
fig.3E
```

```{r, eval=TRUE, message=FALSE, warning=FALSE,fig.width=4, fig.align='center'}
fig.3F <- 
  diff_biomk(MEL_GSE91061,gene = "CXCL13",type = "Treatment",
             p.round=3,log_sc = TRUE,p.pos = c(0.05,0.88),textcol="black") +
  ylim(0,9) +
  scale_y_continuous(labels = scales::number_format(accuracy = 1)) +
  ggtitle("MEL-GSE91061") + 
  ylab("CXCL13 expression (FPKM)") +
  theme(legend.position = "none")
fig.3F
```

```{r, eval=TRUE, message=FALSE, warning=FALSE,fig.width=4, fig.height=3.5, fig.align='center'}
fig.3G <- 
  surv_biomk(MEL_PRJEB23709,gene = "CXCL13",lg.pos=c(0.8,0.92),
           val.pos = c(0,0.2),lg.text = "specific")$plot +
  theme(plot.margin = unit(c(3, 1, 1, 1), "lines"),
        legend.key.height = unit(0,"cm"),
        legend.key.spacing.y = unit(0,"cm"),
        legend.key.size = unit(0,"cm")) +
  ggtitle("MEL-PRJEB23709")
fig.3G
```

```{r fig.3H, eval=TRUE, message=FALSE, warning=FALSE,fig.width=4, fig.height=3.5, fig.align='center'}
fig.3H <-
  surv_biomk(MEL_Nathanson_2017,gene = "CXCL13",lg.pos=c(0.8,0.92),p.round = 3,
             lg.text = "specific",PT_drop = FALSE)$plot +
  theme(plot.margin = unit(c(3, 1, 1, 1), "lines"),
        legend.key.height = unit(0,"cm"),
        legend.key.spacing.y = unit(0,"cm"),
        legend.key.size = unit(0,"cm")) +
  ggtitle("MEL-Nathanson_2017")
fig.3H
```

```{r fig.3I, eval=TRUE, message=FALSE, warning=FALSE,fig.width=4, fig.height=3.5, fig.align='center'}
fig.3I <- 
  surv_biomk(RCC_Braun_2020[,RCC_Braun_2020$Therapy == "anti-PD-1"],
                 gene = "CXCL13",lg.pos=c(0.8,0.92),p.round = 3,
                 lg.text = "specific")$plot +
  theme(plot.margin = unit(c(3, 1, 1, 1), "lines"),
        legend.key.height = unit(0,"cm"),
        legend.key.spacing.y = unit(0,"cm"),
        legend.key.size = unit(0,"cm")) +
  ggtitle("RCC-Braun_2020")
fig.3I
```

```{r fig.3J, eval=TRUE, message=FALSE, warning=FALSE,fig.width=4, fig.align='center'}
fig.3J <- 
  diff_biomk(MEL_PRJEB23709[,MEL_PRJEB23709$Therapy=="anti-PD-1"],
           gene=Average_mean_Sigs$TLS,type = "Response",
           p.round=3,PT_drop = FALSE,p.pos = c(0.05,0.55),
           textcol = "black") +
  ylim(0.8,5.6) +
  ggtitle("MEL-PRJEB23709") +
  ylab("TLS Signature Score") +
  theme(legend.position = "none")
fig.3J
```

```{r fig.3K, eval=TRUE, message=FALSE, warning=FALSE,fig.width=3.5, fig.align='center'}
fig.3K <- 
  roc_biomk(MEL_PRJEB23709[,MEL_PRJEB23709$Therapy=="anti-PD-1"],
            Signature=Average_mean_Sigs$TLS,PT_drop=FALSE,
            textcol = "black",auc.pos = c(0.28,0.4))[[2]] +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank()) +
  ggtitle("MEL-PRJEB23709")
fig.3K
```

```{r fig.3L, eval=TRUE, message=FALSE, warning=FALSE,fig.width=4, fig.height=3.5, fig.align='center'}
fig.3L <-
  surv_biomk(MEL_PRJEB23709[,MEL_PRJEB23709$Therapy=="anti-PD-1"],
             gene=Average_mean_Sigs$TLS,PT_drop=FALSE,
             lg.pos=c(0.8,0.92),p.round = 3,
             lg.text="specific",lg="TLS")$plot +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        plot.margin = unit(c(3, 1, 1, 1), "lines"),
        legend.key.height = unit(0,"cm"),
        legend.key.spacing.y = unit(0,"cm"),
        legend.key.size = unit(0,"cm")) +
  ggtitle("MEL-PRJEB23709")
fig.3L
```

```{r fig.3M, eval=TRUE, message=FALSE, warning=FALSE, fig.align='center'}
fig.3M <-
  compare_biomk(SE=list(MEL_GSE100797,MEL_GSE106128,MEL_GSE115821,
                        MEL_GSE145996,MEL_GSE78220,MEL_GSE91061,MEL_GSE93157,
                        MEL_Nathanson_2017,MEL_phs000452,MEL_PRJEB23709),
                Signature=ipt,method = "Weighted_mean",PT_drop = FALSE) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank())
fig.3M
```

# 3 Identifying tumor microenvironment compositions associated with immunotherapy response (Figure 4)
Tumor microenvironment analysis is crucial for understanding tumor immune evasion mechanisms and predicting the efficacy of immunotherapy. It provides insights into the interactions between tumor cells, immune cells, and stromal components that influence the anti-tumor immune response and treatment outcomes. Here we analyze the relation between tumor microenvironment and immunotherapy outcome.
```{r ,eval=FALSE}
## TIMER
frac1 <- deconv_TME(MEL_GSE78220,method="TIMER")
cell1 <- c("T cells CD4","Neutrophil", "Macrophage","mDCs",
           "B cells", "T cells CD8")
cell_name_filter(frac1)
pie1 <- fraction_pie(cell_name_filter(frac1),
                     feature=factor(cell1, levels = cell1))

## CIBERSORT
frac2 <- deconv_TME(MEL_GSE78220,method="CIBERSORT")
  cell2 <- c("DCs resting", "T cells CD8", "T cells CD4 naive",
           "Macrophages M2", "Yd T cells", "Monocytes",
           "Mast cells resting", "Neutrophils", "Tregs",
           "B cells naive")
pie2 <- fraction_pie(cell_name_filter(frac2[[1]][1:22,]),
                     feature=factor(cell2, levels = cell2))
## MCPCounter
frac3 <- deconv_TME(MEL_GSE78220,method="MCPCounter")
cell3 <- c("CTLs", "Fibroblasts", "T cells", "mDCs", "Monocytic lineage",
           "NK cells", "Endothelial cells", "Neutrophils", "CD8 T cells", "B lineage")
pie3 <- fraction_pie(cell_name_filter(frac3),
                     feature=factor(cell3, levels = cell3))
## xCell
frac4 <- deconv_TME(MEL_GSE78220,method="xCell")
cell4 <- c("Tgd cells", "CD8+ Tem", "Osteoblast", "Megakaryocytes", "CD8+ Tcm", 
           "ly Endothelial cells", "Eosinophils", "mv Endothelial cells", 
           "Endothelial cells", "Smooth muscle")
pie4 <- fraction_pie(cell_name_filter(frac4),
                     feature=factor(cell4, levels = cell4))
## IPS
frac5 <- deconv_TME(MEL_GSE78220,method="IPS")
cell5 <- c("IPS", "MHC", "CP", "AZ", "SC", "EC")
bar5 <- 
draw_bar(cell_name_filter(frac5),
         feature=factor(cell5, levels = cell5))
## EPIC
frac6 <- deconv_TME(MEL_GSE78220,method="epic")
cell6 <- c("NKcells", "CD4_Tcells", "CD8_Tcells", "Bcells", "CAFs",
           "Macrophages", "Endothelial", "otherCells")
pie6 <- fraction_pie(cell_name_filter(frac6),
                     feature=factor(cell6, levels = cell6))
## ESTIMATE
frac7 <- deconv_TME(MEL_GSE78220,method="ESTIMATE")
cell7 <- c("StromalScore", "ESTIMATEScore", "TumorPurity", "ImmuneScore")
bar7 <- draw_bar(cell_name_filter(frac7),
                 feature=factor(cell7, levels = cell7))
## ABIS
frac8 <- deconv_TME(MEL_GSE78220,method="ABIS")
cell8 <-  c("Macrophages M1", "Plasma cells", "CD4+ T memory activated", 
            "T cells follicular helper", "DCs activated", "T cells CD8", 
            "NK cells activated", "Neutrophils", "Tregs", "B cells naive")
pie8 <- fraction_pie(cell_name_filter(frac8),
                     feature=factor(cell8, levels = cell8))
## ConsensusTME
frac9 <- deconv_TME(MEL_GSE78220,method="ConsensusTME")
cell9 <- c("T cells CD4", "NK cells", "Yd T cells", "Mast cells",
           "T cells CD8", "Immune Score", "Tregs", "Plasma cells", 
           "B cells", "Endothelial")
pie9 <- fraction_pie(cell_name_filter(frac9),
                     feature=factor(cell9, levels = cell9))
## quanTIseq
frac10 <- deconv_TME(MEL_GSE78220,method="quanTIseq")
cell10 <- c("Neutrophils", "T cells CD4", "DCs", "Tregs", "Other", "B cells",
            "Macrophages.M2", "Macrophages.M1", "T cells CD8", "Monocytes")
pie10 <- fraction_pie(cell_name_filter(frac10),
                      feature=factor(cell10,levels = cell10))
bar_IPS <- 
  gridExtra::grid.arrange(bar5[[1]],bar5[[2]],bar5[[3]],
                          bar5[[4]],bar5[[5]],bar5[[6]],nrow=1)
bar_ESTIMATE <- 
  gridExtra::grid.arrange(bar7[[1]],bar7[[2]],
                          bar7[[3]],bar7[[4]],nrow=1)
grob_list <-
  list(pie1, pie2, pie3, pie4, pie6, pie8, pie9, pie10,
       bar_IPS, bar_ESTIMATE)
```

```{r fig.4Adata, eval=TRUE, message=FALSE, warning=FALSE, cache=TRUE, include=FALSE}
## TIMER
frac1 <- deconv_TME(MEL_GSE78220,method="TIMER")
cell1 <- c("T cells CD4","Neutrophil", "Macrophage","mDCs",
           "B cells", "T cells CD8")
cell_name_filter(frac1)
pie1 <- fraction_pie(cell_name_filter(frac1),
                     feature=factor(cell1, levels = cell1))

## CIBERSORT
frac2 <- deconv_TME(MEL_GSE78220,method="CIBERSORT")
  cell2 <- c("DCs resting", "T cells CD8", "T cells CD4 naive",
           "Macrophages M2", "Yd T cells", "Monocytes",
           "Mast cells resting", "Neutrophils", "Tregs",
           "B cells naive")
pie2 <- fraction_pie(cell_name_filter(frac2[[1]][1:22,]),
                     feature=factor(cell2, levels = cell2))
## MCPCounter
frac3 <- deconv_TME(MEL_GSE78220,method="MCPCounter")
cell3 <- c("CTLs", "Fibroblasts", "T cells", "mDCs", "Monocytic lineage",
           "NK cells", "Endothelial cells", "Neutrophils", "CD8 T cells", "B lineage")
pie3 <- fraction_pie(cell_name_filter(frac3),
                     feature=factor(cell3, levels = cell3))
## xCell
frac4 <- deconv_TME(MEL_GSE78220,method="xCell")
cell4 <- c("Tgd cells", "CD8+ Tem", "Osteoblast", "Megakaryocytes", "CD8+ Tcm", 
           "ly Endothelial cells", "Eosinophils", "mv Endothelial cells", 
           "Endothelial cells", "Smooth muscle")
pie4 <- fraction_pie(cell_name_filter(frac4),
                     feature=factor(cell4, levels = cell4))
## IPS
frac5 <- deconv_TME(MEL_GSE78220,method="IPS")
cell5 <- c("IPS", "MHC", "CP", "AZ", "SC", "EC")
bar5 <- 
draw_bar(cell_name_filter(frac5),
         feature=factor(cell5, levels = cell5))
## EPIC
frac6 <- deconv_TME(MEL_GSE78220,method="epic")
cell6 <- c("NKcells", "CD4_Tcells", "CD8_Tcells", "Bcells", "CAFs",
           "Macrophages", "Endothelial", "otherCells")
pie6 <- fraction_pie(cell_name_filter(frac6),
                     feature=factor(cell6, levels = cell6))
## ESTIMATE
frac7 <- deconv_TME(MEL_GSE78220,method="ESTIMATE")
cell7 <- c("StromalScore", "ESTIMATEScore", "TumorPurity", "ImmuneScore")
bar7 <- draw_bar(cell_name_filter(frac7),
                 feature=factor(cell7, levels = cell7))
## ABIS
frac8 <- deconv_TME(MEL_GSE78220,method="ABIS")
cell8 <-  c("Macrophages M1", "Plasma cells", "CD4+ T memory activated", 
            "T cells follicular helper", "DCs activated", "T cells CD8", 
            "NK cells activated", "Neutrophils", "Tregs", "B cells naive")
pie8 <- fraction_pie(cell_name_filter(frac8),
                     feature=factor(cell8, levels = cell8))
## ConsensusTME
frac9 <- deconv_TME(MEL_GSE78220,method="ConsensusTME")
cell9 <- c("T cells CD4", "NK cells", "Yd T cells", "Mast cells",
           "T cells CD8", "Immune Score", "Tregs", "Plasma cells", 
           "B cells", "Endothelial")
pie9 <- fraction_pie(cell_name_filter(frac9),
                     feature=factor(cell9, levels = cell9))
## quanTIseq
frac10 <- deconv_TME(MEL_GSE78220,method="quanTIseq")
cell10 <- c("Neutrophils", "T cells CD4", "DCs", "Tregs", "Other", "B cells",
            "Macrophages.M2", "Macrophages.M1", "T cells CD8", "Monocytes")
pie10 <- fraction_pie(cell_name_filter(frac10),
                      feature=factor(cell10,levels = cell10))
bar_IPS <- 
  gridExtra::grid.arrange(bar5[[1]],bar5[[2]],bar5[[3]],
                          bar5[[4]],bar5[[5]],bar5[[6]],nrow=1)
bar_ESTIMATE <- 
  gridExtra::grid.arrange(bar7[[1]],bar7[[2]],
                          bar7[[3]],bar7[[4]],nrow=1)
grob_list <-
  list(pie1, pie2, pie3, pie4, pie6, pie8, pie9, pie10,
       bar_IPS, bar_ESTIMATE)
```

```{r fig.4A, eval=TRUE, fig.width=26, fig.height=23}
gridExtra::grid.arrange(grobs = grob_list, ncol = 1, 
                        heights = c(1, 1, 1, 1, 1, 1, 1, 1, 2, 2))
```

```{r fig.4B, eval=TRUE, message=FALSE, warning=FALSE, width=4}
## TIMER
TM <- deconv_TME(MEL_GSE91061,method = "TIMER")
TM1 <- cell_name_filter(TM)
TM_SE <- SummarizedExperiment(assays=SimpleList(TM1),
                              colData=colData(MEL_GSE91061))
fig.4B <- browse_biomk(SE=TM_SE)
fig.4B
```

```{r fig.4C, eval=TRUE, message=FALSE, warning=FALSE, width=4}
## CIBERSORT
CISORT <- deconv_TME(MEL_GSE91061,
                     method="CIBERSORT")
CISORT1 <- cell_name_filter(CISORT[[1]][1:22,])
CIBER_SE <- SummarizedExperiment(assays=SimpleList(CISORT1),
                                 colData=colData(MEL_GSE91061))
fig.4C <- browse_biomk(SE=CIBER_SE)
fig.4B
```

```{r fig.4D, eval=TRUE, message=FALSE, warning=FALSE, width=4}
## MCPCounter
MCP <- deconv_TME(MEL_GSE91061,
                  method="MCPCounter")
MCP1 <- cell_name_filter(MCP)
MCP_SE <- SummarizedExperiment(assays=SimpleList(MCP1),
                               colData=colData(MEL_GSE91061))
fig.4D <- browse_biomk(SE=MCP_SE)
fig.4D
```

```{r , eval=TRUE, message=FALSE, warning=FALSE, include=FALSE,cache=TRUE}
## xCell
xCl <- deconv_TME(MEL_GSE91061,
                  method="xCell")
```
```{r fig.4E, eval=TRUE, message=FALSE, warning=FALSE, width=4}
xCl1 <- cell_name_filter(xCl)
xCl_SE <- SummarizedExperiment(assays=SimpleList(xCl1),
                               colData=colData(MEL_GSE91061))
fig.4E <- browse_biomk(SE=xCl_SE)
fig.4E
```

```{r fig.4F, eval=TRUE, message=FALSE, warning=FALSE, width=4}
## IPS
Ips <- deconv_TME(MEL_GSE91061,
                  method="IPS")
Ips_SE <- SummarizedExperiment(assays=SimpleList(Ips),
                               colData=colData(MEL_GSE91061))
fig.4F <- browse_biomk(SE=Ips_SE)
fig.4F
```

```{r fig.4G, eval=TRUE, message=FALSE, warning=FALSE, width=4}
## EPIC
Epc <- deconv_TME(MEL_GSE91061,
                  method="epic")
Epc_SE <- SummarizedExperiment(assays=SimpleList(Epc),
                               colData=colData(MEL_GSE91061))
fig.4G <- browse_biomk(SE=Epc_SE)
fig.4G
```

```{r fig.4H, eval=TRUE, message=FALSE, warning=FALSE, width=4}
## ESTIMATE
Est <- deconv_TME(MEL_GSE91061,
                  method="ESTIMATE")
Est_SE <- SummarizedExperiment(assays=SimpleList(Est),
                               colData=colData(MEL_GSE91061))
fig.4H <- browse_biomk(SE=Est_SE)
fig.4H
```

```{r fig.4I, eval=TRUE, message=FALSE, warning=FALSE, width=4}
## ABIS
Abs <- deconv_TME(MEL_GSE91061,
                  method="ABIS")
Abs1 <- cell_name_filter(Abs)
Abs_SE <- SummarizedExperiment(assays=SimpleList(Abs1),
                               colData=colData(MEL_GSE91061))
fig.4I <- browse_biomk(SE=Abs_SE)
fig.4I
```

```{r fig.4J, eval=TRUE, message=FALSE, warning=FALSE, width=4}
## ConsensusTME
CTM <- deconv_TME(MEL_GSE91061,
                  method="ConsensusTME")
CTM1 <- cell_name_filter(CTM)
CTM_SE <- SummarizedExperiment(assays=SimpleList(CTM1),
                               colData=colData(MEL_GSE91061))
fig.4J <- browse_biomk(SE=CTM_SE)
fig.4J
```

```{r fig.4K, eval=TRUE, message=FALSE, warning=FALSE, width=4}
## quanTIseq
qTI <- deconv_TME(MEL_GSE91061,
                  method="quanTIseq")
qTI1 <- cell_name_filter(qTI)
qTI_SE <- SummarizedExperiment(assays=SimpleList(qTI1),
                               colData=colData(MEL_GSE91061))
fig.4K <- browse_biomk(SE=qTI_SE)
fig.4K
```

```{r fig.4L, eval=TRUE, message=FALSE, warning=FALSE,fig.width=4, fig.height=3.5, fig.align='center'}
## L
t1 <- surv_biomk(CIBER_SE,gene = "B cells naive",lg.pos=c(0.8,0.92),
                 val.pos = c(0,0.2),lg.text = "specific",PT_drop = FALSE,
                 p.round = 3)
fig.4L <- t1$plot + theme(axis.title.y = element_blank(),
                        axis.title.x = element_blank(),
                        plot.margin = unit(c(3, 1, 1, 1), "lines"),
                        legend.key.height = unit(0,"cm"),
                        legend.key.spacing.y = unit(0,"cm"),
                        legend.key.size = unit(0,"cm"))
fig.4L
```

```{r fig.4M, eval=TRUE, message=FALSE, warning=FALSE,fig.width=4, fig.height=3.5, fig.align='center'}
## M
t2 <- surv_biomk(CIBER_SE,gene = "Monocytes",lg.pos=c(0.8,0.92),
                 val.pos = c(0,0.2),lg.text = "specific",PT_drop = FALSE,
                 p.round = 3)
fig.4M <- t2$plot + theme(axis.title.y = element_blank(),
                     axis.title.x = element_blank(),
                     plot.margin = unit(c(3, 1, 1, 1), "lines"),
                     legend.key.height = unit(0,"cm"),
                     legend.key.spacing.y = unit(0,"cm"),
                     legend.key.size = unit(0,"cm"))
fig.4M
```

# 4 Constructing immunotherapy response prediction model (Figure 5)
We then construct a prediction Model module for robust immunotherapy response prediction. 
```{r fig.5data, result='hide',eval=TRUE, message=FALSE, warning=FALSE, cache=TRUE}
library(tigeR)
library(SummarizedExperiment)
library(magrittr)
# Data preparation
SE_origin <- cbind(MEL_GSE91061,
                   MEL_phs000452,
                   MEL_Nathanson_2017)

exp <-
  dataProcess_SE(data_standardization(SE_origin, type = c(1,2,3,4)),
                 Signature = NULL,rmBE = TRUE,response_NR=TRUE,
                 turn2HL=FALSE)
cf <-
  dataProcess_SE(data_standardization(SE_origin,type=c(1,2)),
                        Signature = NULL,rmBE = FALSE,response_NR=TRUE,
                        turn2HL=FALSE) %>%
  TIMER_SE(type="SKCM") %>%
  to1()

sg <-
  dataProcess_SE(data_standardization(SE_origin,type=c()),
                 Signature = NULL,rmBE = FALSE,response_NR=TRUE,
                 turn2HL=FALSE) %>%
  score_biomk_SE(sg_SE,PT_drop = FALSE) %>%
  to1()


final_SE <- rbind(exp,cf,sg)

set.seed(6)
idx <- sample(1:275,size=187)
SE_obj_train <- final_SE[,idx]
SE_obj_test <- final_SE[,-idx]


m <- t(
  apply(assay(exp)[,idx], 1, function(x){
    if(length(which(x==0))*5>length(x))
      return(rep(NA,length(x)))
    else
      return(x)
  }))
colnames(m) <- colnames(assay(exp)[,idx])
vars <- na.omit(
  apply(m,1,var,na.rm=TRUE))
selected_genes <- names(vars[vars>0.1])

NB_model <- build_Model(SE_obj_train,
                        Model = "NB",
                        feature_genes = c(selected_genes,
                                          rownames(cf),
                                          rownames(sg)),
                        rmBE = FALSE,
                        response_NR = TRUE,
                        laplace=0)

RF_model <- build_Model(SE_obj_train,
                        Model = "RF",
                        feature_genes = c(selected_genes,
                                          rownames(cf),
                                          rownames(sg)),
                        rmBE = FALSE,
                        response_NR = TRUE)

SVM_model <- build_Model(SE_obj_train,
                         Model = "SVM",
                         feature_genes = c(selected_genes,
                                           rownames(cf),
                                           rownames(sg)),
                         rmBE = FALSE,
                         response_NR = TRUE)

CC_model <- build_Model(SE_obj_train,
                        Model = "CC",
                        feature_genes = c(selected_genes,
                                          rownames(cf),
                                          rownames(sg)),
                        rmBE = FALSE,
                        response_NR = TRUE)
ADB_model <- build_Model(SE_obj_train,
                         Model = "ADB",
                         feature_genes = c(selected_genes,
                                           rownames(cf),
                                           rownames(sg)),
                         rmBE = FALSE,
                         response_NR = TRUE)
LGB_model <- build_Model(SE_obj_train,
                         Model = "LGB",
                         feature_genes = c(selected_genes,
                                           rownames(cf),
                                           rownames(sg)),
                         rmBE = FALSE,
                         response_NR = TRUE)
LGT_model <- build_Model(SE_obj_train,
                         Model = "LGT",
                         feature_genes = c(selected_genes,
                                           rownames(cf),
                                           rownames(sg)),
                         rmBE = FALSE,
                         response_NR = TRUE)
```

```{r, eval=TRUE, message=FALSE, warning=FALSE,fig.width=3.5,fig.align='center'}
## B
pp1=test_Model(NB_model,SE=SE_obj_train)
pp2=test_Model(SVM_model,SE=SE_obj_train)
pp3=test_Model(RF_model,SE=SE_obj_train)
pp4=test_Model(CC_model,SE=SE_obj_train)
pp5=test_Model(ADB_model,SE=SE_obj_train)
pp6=test_Model(LGB_model,SE=SE_obj_train)
pp7=test_Model(LGT_model,SE=SE_obj_train)

fig.5B <-
  compare_roc(list(pp1[[1]],pp2[[1]],pp3[[1]],
                   pp4[[1]],pp5[[1]],pp6[[1]],pp7[[1]])) +
  ggtitle("Train set (n = 187)") +
  theme(plot.title = element_text(hjust = 0.5, size = 14, face="bold"))
fig.5B
```

```{r, eval=TRUE, message=FALSE, warning=FALSE,fig.width=3.5,fig.align='center'}
## C
p1=test_Model(NB_model,SE=SE_obj_test)
p2=test_Model(SVM_model,SE=SE_obj_test)
p3=test_Model(RF_model,SE=SE_obj_test)
p4=test_Model(CC_model,SE=SE_obj_test)
p5=test_Model(ADB_model,SE=SE_obj_test)
p6=test_Model(LGB_model,SE=SE_obj_test)
p7=test_Model(LGT_model,SE=SE_obj_test)

fig.5C <-
  compare_roc(list(p1[[1]],p2[[1]],p3[[1]],
                   p4[[1]],p5[[1]],p6[[1]],p7[[1]])) +
  ggtitle("Test set (n = 88)") +
  theme(plot.title = element_text(hjust = 0.5, size = 14, face="bold"))
fig.5C
```

```{r, eval=TRUE, message=FALSE, warning=FALSE,fig.width=3.5,fig.align='center'}
## D
ipt <- RF_model$importance[,1]
fig.5D <-
  roc_biomk(SE=MEL_GSE78220,Signature = ipt,
            method = "Weighted_mean",PT_drop = FALSE,
            textcol = "black",auc.pos = c(0.28,0.4))[[2]] +
  ggtitle("MEL-GSE78220")
fig.5D
```

```{r, eval=TRUE, message=FALSE, warning=FALSE,fig.width=4, height=3.5, fig.align='center'}
## E
fig.5E <-
  surv_biomk(MEL_GSE78220,gene = ipt, method="Weighted_mean",PT_drop=TRUE,
             lg.pos=c(0.6,0.98), p.round = 3,lg.text = "specific",
             lg="Customed Signature")$plot +
  ggtitle("MEL-GSE78220") +
  theme(plot.margin = unit(c(3, 1, 1, 1), "lines"),
        legend.key.height = unit(0,"cm"),
        legend.key.spacing.y = unit(0,"cm"),
        legend.key.size = unit(0,"cm"))
fig.5E
```

```{r, eval=TRUE, message=FALSE, warning=FALSE, fig.width=9,fig.height=4.5,fig.align='center'}
## F
F <-
  pred_response(SE=MEL_GSE93157,Signature = ipt,
                method = "Weighted_mean",threshold = 0.8,
                PT_drop = FALSE,sort_by = "Customed.Signature",
                group_by = "Customed.Signature",show.real = TRUE,
                rankscore = FALSE)
F
